% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
\documentclass[nz-terms]{subfiles}
\begin{document}

\section{Charges and Payment}

\begin{enumerate}
\item The Supplier's price quote ("the Fee") is set out in the Agreement and
will, unless accepted, expire thirty days from the date of the Agreement.
\item The Purchaser shall pay twenty five percent of the Fee on acceptance of
the Agreement. Subsequent work, after subtracting the twenty five percent of
the Fee paid on acceptance of the Agreement shall be invoiced on the basis
described in the Agreement.
\item Unless an alternative payment schedule is specified in the Agreement or
otherwise attached to the Agreement, each invoice shall be due and payable by
the Purchaser within 14 days following the date of the invoice.
\item Disbursements not specifically included in the Fee, such as reasonable
travel and accommodation expenses and tasks performed on a time and materials
basis, will be charged in addition to the Fee where applicable.
\item Unless otherwise specified, all prices and quotes exclude Goods and
Services Tax and other government taxes and levies where properly due.
\item If payment is not received by the Supplier by the due date, then, without
prejudice to the Supplier's other legal remedies:
    \begin{enumerate}
    \item The Supplier may charge default interest on the overdue monies at the
    current commercial overdraft rate charged by our trading bank.
    \item The Purchaser shall indemnify the Supplier in respect of any legal
    costs and expenses reasonably incurred by the Supplier in collecting or
    attempting to collect any overdue amount (together with any interest
    payable).
    \end{enumerate}
\item Termination of the Agreement for any reason shall not affect the
Purchaser's liability to pay the Supplier in relation to any costs incurred
and work performed in accordance with the Agreement prior to the date of
termination, and the Supplier may invoice the Purchaser for such costs and
work.
\end{enumerate}

\end{document}