% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
\documentclass[nz-terms]{subfiles}
\begin{document}

\section{Confidentiality}

\begin{enumerate}
\item Confidential Information includes all business, personal, strategic and
technical information or data, in any form whatsoever, disclosed to or
received by you pursuant to the completion of the Agreement (whether in
writing, verbally, or by any other means and whether directly or indirectly).
This includes, by way of example and not limitation, the terms of the
Agreement, all information pertaining to the affairs, polices, products,
software, operations, processes, costings, pricing methods, personnel, plans
or intentions, product information, know-how, intellectual property, design
rights, trades secrets, market opportunities and business affairs of The
Supplier.
\item Any and all Confidential Information received by the Purchaser from the
Supplier shall be held and kept confidential by the Purchaser and shall be
used by the Purchaser solely for the strict purpose of performing the
Purchaser's obligations pursuant to the Agreement. Confidential Information
shall not be disclosed by the Purchaser to any third party except with, and
on the terms of, prior written consent of the Supplier or as required by law.
\item The Supplier's Confidential Information remains the property of the
Supplier and no right, entitlement or interest in the Supplier's Confidential
Information is extended or conveyed to the Purchaser. At the Supplier's
request, and upon termination of the Agreement, The Purchaser must ensure
that all of the Supplier's Confidential Information is either destroyed or
returned as requested, and must, if requested by the Supplier, forthwith
certify in writing that this has occurred.
\item Any and all Confidential Information received by the Supplier from the
Purchaser shall be held and kept confidential by the Supplier and shall be
used by the Supplier solely for the strict purpose of performing the
Supplier's obligations pursuant to the Agreement. Confidential Information
shall not be disclosed by the Supplier to any third party except with, and on
the terms of, prior written consent of the Purchaser or as required by law.
\item The Purchaser's Confidential Information remains the property of the
Purchaser and no right, entitlement or interest in the Purchaser's
Confidential Information is extended or conveyed to the Supplier. At the
Purchaser's request, and upon termination of the Agreement, the Supplier must
ensure that all of the Purchaser's Confidential Information is either
destroyed or returned as requested, and must, if requested by the Purchaser,
forthwith certify in writing that this has occurred.
\end{enumerate}

\end{document}