% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
\documentclass[nz-terms]{subfiles}
\begin{document}

\section{Intellectual Property}

\begin{enumerate}
\item The Supplier, subject to payment in full of all sums owing, grants the
Purchaser a non-exclusive licence in respect of all pre-existing material of
the Supplier, which comprises the Deliverables upon completion of the
Project, including but not limited to The Supplier's application software,
library code, templates and data.
\item The Purchaser shall provide all logos, graphics, pictures, text and all
other relevant information to the Supplier in a timely fashion to allow
completion of the Project by the date specified in the Agreement.
\item The Purchaser warrants that all materials provided to the Supplier for the
purposes of the Project:
    \begin{enumerate}
    \item Do not infringe Intellectual Property rights of any other person;
    \item Are not unlawful, objectionable, offensive, threatening, abusive or
    defamatory; and
    \item Do not comprise and cannot be used for any purpose or activity which
    is of an illegal, fraudulent or defamatory nature.
    \end{enumerate}
\item The Purchaser agrees that the copyright in all source code, software,
information, documentation and techniques developed to deliver the Project
resides with the Supplier and that the Purchaser is granted a non-exclusive
license to the instance of the Deliverable developed as per the Agreement
only. The Purchaser may request copyright of specific elements (e.g. images,
source code files) of the Project. These elements, if any, are described in
an attached schedule.
\item The Supplier reserves the right to release any source code, software,
information, documentation and techniques that it holds the copyright to
under any licence it chooses. The Supplier agrees to make every reasonable
effort to ensure that any such release preserves the competitive advantage
and brand identity of the Purchaser.
\item The Purchaser may request that the Supplier not release aspects of the
Project, related to look and feel or specific algorithms developed for the
purposes of the Project. Those aspects, if any, are described in an attached
schedule.
\item The Supplier makes every reasonable effort to honour the licence terms of
third party software incorporated into the Project and agrees to alert the
Purchaser to the implications of any third party licences.
\item The Purchaser agrees to grant the Supplier a limited licence to reproduce
graphical representations, e.g. screen shots, of the Deliverable via the
world wide web or by any other medium as part of the Supplier's portfolio for
the purposes of marketing and demonstration of capabilities.
\item The Supplier agrees to grant the Purchaser a limited license to reproduce
its trademarked brand (logo, company name, etc..) for marketing, reporting,
or demonstration purposes.
\end{enumerate}

\end{document}